Forecasting the 2024 U.S. Presidential Election

### 2024-11-02 paper/paper.qmd
words changed to follow prose guideline

This statistical approach effectively bridges the gap between state-level polling data and the Electoral College outcome. By employing multiple linear regression models to predict polling percentages and integrating these predictions with the electoral vote framework, we provide a nuanced analysis of potential election results. This methodology respects the intricacies of the U.S. electoral system and offers valuable insights into how predicted voter support may translate into electoral success.

>>>>

This statistical approach effectively connects state-level polling data to Electoral College projections. By employing multiple linear regression models to predict polling percentages and integrating these predictions with the electoral vote framework, we provide a detailed analysis of potential election results. This methodology reflects the structure of the U.S. electoral system and offers valuable insights into how predicted voter support may translate into electoral success.
